---
title: CV
name: Graham
surname: Buhrman
position: "Doctoral Student"
address: "Educational Sciences 1025 W Johnson Street"
phone: +1 919 452 2190
email: "gwbuhrman@gmail.com"
twitter: GrahamBuhrman
github: GrahamBuhrman
linkedin: graham-buhrman
orcid: 0000-0003-4125-7171
headcolor: "414141"
docname: "Curriculum Vitae"
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
    show_footer: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(vitae)
library(tibble)
library(googlesheets4)
library(dplyr)
library(tidyverse)
library(stringr)

gs4_auth(email = "gwbuhrman@gmail.com")

```

# Research Interests

As a doctoral student, I am interested in further honing my research interests. Currently, I am curious about the applications of natural language processing to causal inference in the social and behavioral sciences, and in the impacts of missing data on estimation of causal effects from observational data. 

# Education

```{r education}

googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/11AWQDqQletA1Jd9_lJfK1HkLcubAWxugTRLaQohbL80/edit#gid=0",
                          sheet = "Education") %>%
  vitae::detailed_entries(what = Degree,
                          when = Dates,
                          where = Location,
                          with = University,
                          why = Details)

```

# Professional Experience

```{r professional}

googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/11AWQDqQletA1Jd9_lJfK1HkLcubAWxugTRLaQohbL80/edit#gid=0",
                          sheet = "Professional Experience") %>%
  vitae::detailed_entries(what = Title,
                          when = Dates,
                          where = Location,
                          with = Institution,
                          why = Details)

```

# Research Experience

```{r research}

googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/11AWQDqQletA1Jd9_lJfK1HkLcubAWxugTRLaQohbL80/edit#gid=0",
                          sheet = "Research Experience") %>%
  vitae::detailed_entries(what = Lab,
                          when = Dates,
                          where = Location,
                          with = Institution,
                          why = Details)

```

# Published Articles

```{r published_articles}

googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/11AWQDqQletA1Jd9_lJfK1HkLcubAWxugTRLaQohbL80/edit#gid=255827046", 
                          sheet = "Publications") %>%
  filter(category == "peer-published") %>%
  select(-category) %>%
  RefManageR::as.BibEntry() %>%
  RefManageR::WriteBib("published_articles.bib", biblatex = T)

vitae::bibliography_entries("published_articles.bib") %>%
  arrange(desc(issued))

```

# Manuscripts Under Review

```{r under_review}

googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/11AWQDqQletA1Jd9_lJfK1HkLcubAWxugTRLaQohbL80/edit#gid=255827046", 
                          sheet = "Publications") %>%
  filter(category == "under-review") %>%
  select(-category) %>%
  RefManageR::as.BibEntry() %>%
  RefManageR::WriteBib("under_review.bib", biblatex = T)

vitae::bibliography_entries("under_review.bib") %>%
  arrange(desc(issued))

```

# Presentations and Posters

```{r presentations}

googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/11AWQDqQletA1Jd9_lJfK1HkLcubAWxugTRLaQohbL80/edit#gid=0",
                          sheet = "Presentations") %>%
  vitae::detailed_entries(what = Title,
                          when = Dates,
                          where = Location,
                          with = Conference,
                          why = Details)

```

# Awards and Achievements

## Grants

```{r grants}

googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/11AWQDqQletA1Jd9_lJfK1HkLcubAWxugTRLaQohbL80/edit#gid=0",
                          sheet = "Grants") %>%
  vitae::detailed_entries(what = Grant,
                          when = Year,
                          with = From,
                          why = Details)

```

## Awards

```{r awards}

googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/11AWQDqQletA1Jd9_lJfK1HkLcubAWxugTRLaQohbL80/edit#gid=0",
                          sheet = "Awards") %>%
  vitae::detailed_entries(what = Award,
                          when = Year,
                          with = From,
                          why = Details)

```

## Scholarships

```{r scholarships}

googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/11AWQDqQletA1Jd9_lJfK1HkLcubAWxugTRLaQohbL80/edit#gid=0",
                          sheet = "Scholarships") %>%
  vitae::detailed_entries(what = Scholarship,
                          when = Year,
                          with = From,
                          why = Details)

```

# Relevant Skills

\begin{cvskills}
  \cvskill
    {Programming:}
    {Python, R, SAS, HTML/CSS}
  \cvskill
    {Data Analysis:}
    {Processing/Cleaning, Visualization, Modelling, Inference, Communication}
  \end{cvskills}
  
